---
title: "探索模型解释的标准化流程"
author: "LIXINWU"
date: "2019年3月14号"
output: html_document
---

```{r setup,echo=FALSE,message=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(DT)
library(DALEX)
library(dplyr)
library(tidyr)
library(tidyverse)
library(survival)
```

#Build A Model
    通过泰坦尼克号生存的数据进行挖掘,建立模型,探索模型解释的标准化维度.

## Model for Titanic survival 

```{r message=FALSE,echo=FALSE,warning=FALSE}
# prepare model
library(randomForest)
load("D:/R_pluraslight/titanic.rda")
titanic <- na.omit(titanic)
model_titanic_rf <- randomForest(survived=="yes" ~ gender + age + class+embarked+ fare + sibsp + parch,  data = titanic)
model_titanic_rf
```



##Explanier for Titanic survival 
```{r echo=FALSE,message=FALSE,warning=FALSE}
explain_titanic_rf <- explain(model_titanic_rf, 
                      data = titanic[,-9],
                      y = titanic$survived == "yes", 
                      label = "Random Forest v7")
```


##Variable importance plots
```{r echo=FALSE,warning=FALSE,message=FALSE}
vi_rf <- variable_importance(explain_titanic_rf)
#head(vi_rf)
plot(vi_rf)
```

##Variable effects

###Age 
```{r echo=FALSE,message=FALSE,warning=FALSE}
vr_age  <- variable_response(explain_titanic_rf, variable =  "age")
#head(vr_age)
plot(vr_age, use_facets = TRUE)
```

###Class

```{r echo=FALSE,warning=FALSE,message=FALSE}
vr_class  <- variable_response(explain_titanic_rf, variable =  "class")
plot(vr_class)
```

###Fare
```{r echo=FALSE,warning=FALSE,message=FALSE}
vr_fare  <- variable_response(explain_titanic_rf, variable =  "fare")
plot(vr_fare, use_facets = TRUE)
```

###Embarked
```{r echo=FALSE,warning=FALSE,message=FALSE}
vr_embarked  <- variable_response(explain_titanic_rf, variable =  "embarked")
plot(vr_embarked)
```

##Instance level explanations
```{r echo=FALSE,warning=FALSE,message=FALSE}
new_passanger <- data.frame(
  class = factor("1st", levels = c("1st", "2nd", "3rd", "deck crew", "engineering crew", "restaurant staff", "victualling crew")),
  gender = factor("male", levels = c("female", "male")),
  age = 8,
  sibsp = 0,
  parch = 0,
  fare = 72,
  embarked = factor("Southampton", levels = c("Belfast", "Cherbourg", "Queenstown", "Southampton"))
)

sp_rf <- single_prediction(explain_titanic_rf, new_passanger)
plot(sp_rf)
```

#More Models 
###Logistic regression 

```{r echo=FALSE,WARNONG=FALSE,message=FALSE}
library("rms")
model_titanic_lmr <- lrm(survived == "yes" ~ class + gender + rcs(age) + sibsp +
                   parch + fare + embarked, titanic)
explain_titanic_lmr <- explain(model_titanic_lmr, data = titanic, 
                       y = titanic$survived == "yes", 
                       predict_function = function(m,x) predict(m, x, type="fitted"),
                       label = "Logistic regression")
```


###Generalized Boosted Models 
```{r echo=FALSE,message=FALSE,warning=FALSE}
library("gbm")
model_titanic_gbm <- gbm(survived == "yes" ~ class + gender + age + sibsp +
                     parch + fare + embarked, data = titanic, n.trees = 15000)

explain_titanic_gbm <- explain(model_titanic_gbm, data = titanic, 
                       y = titanic$survived == "yes", 
                       predict_function = function(m,x) predict(m, x, n.trees = 15000, type = "response"),
                       label = "Generalized Boosted Models")
```

###Support Vector Machines (SVM)

```{r echo=FALSE,message=FALSE,warning=FALSE}
library("e1071")
model_titanic_svm <- svm(survived == "yes" ~ class + gender + age + sibsp +
                     parch + fare + embarked, data = titanic, 
             type = "C-classification", probability = TRUE)
explain_titanic_svm <- explain(model_titanic_svm, data = titanic, 
                       y = titanic$survived == "yes", 
                       label = "Support Vector Machines")
```

###k-Nearest Neighbours (kNN)
```{r echo=FALSE,warning=FALSE,message=FALSE}
library("caret")
model_titanic_knn <- knn3(survived == "yes" ~ class + gender + age + sibsp +
                     parch + fare + embarked, data = titanic, k = 5)
explain_titanic_knn <- explain(model_titanic_knn, data = titanic, 
                       y = titanic$survived == "yes", 
                       predict_function = function(m,x) predict(m, x)[,2],
                       label = "k-Nearest Neighbours")
###Variable performance
vi_rf <- variable_importance(explain_titanic_rf)
vi_lmr <- variable_importance(explain_titanic_lmr)
vi_gbm <- variable_importance(explain_titanic_gbm)
vi_svm <- variable_importance(explain_titanic_svm)
vi_knn <- variable_importance(explain_titanic_knn)

plot(vi_rf, vi_lmr, vi_gbm, vi_svm, vi_knn, bar_width = 4)
```

###Single variable 
```{r echo=FALSE,message=FALSE,warning=FALSE}
vr_age_rf  <- variable_response(explain_titanic_rf, variable =  "age")
vr_age_lmr  <- variable_response(explain_titanic_lmr, variable =  "age")
vr_age_gbm  <- variable_response(explain_titanic_gbm, variable =  "age")
vr_age_svm  <- variable_response(explain_titanic_svm, variable =  "age")
vr_age_knn  <- variable_response(explain_titanic_knn, variable =  "age")
plot(vr_age_rf, vr_age_lmr, vr_age_gbm, vr_age_svm, vr_age_knn)
```


###Instance level explanations
```{r echo=FALSE,message=FALSE,warning=FALSE}
sp_rf <- single_prediction(explain_titanic_rf, new_passanger)
sp_lmr <- single_prediction(explain_titanic_lmr, new_passanger)
sp_gbm <- single_prediction(explain_titanic_gbm, new_passanger)
sp_svm <- single_prediction(explain_titanic_svm, new_passanger)
sp_knn <- single_prediction(explain_titanic_knn, new_passanger)
plot(sp_rf, sp_lmr, sp_gbm, sp_svm, sp_knn)
```


```{r echo=FALSE,message=FALSE,warning=FALSE}
sessionInfo()
```
